<<<<<<< Updated upstream
\documentclass[11pt, a4paper, colorlinks=true, linkcolor=blue]{moderncv}
\moderncvtheme{banking}
% \usepackage[sfdefault, light]{FiraSans}
\usepackage[default, oldstyle, scale=0.95]{opensans}
\usepackage[top=1.1cm, bottom=1.5cm, right=1cm, left=1.24cm]{geometry}
\linespread{1.08}
=======
% \documentclass[11pt, a4paper, colorlinks=true, linkcolor=blue]{moderncv}
% \moderncvtheme{banking}
\documentclass{pats-resume}
% \usepackage[sfdefault, light]{FiraSans}
% \usepackage[top=0.6cm, bottom=1.5cm, right=1cm, left=1cm]{geometry}
% \recomputelengths
>>>>>>> Stashed changes

% personal data
\setname{Dilawar Singh}
% \setphone{+91 910 875 0527}
\setemail{dilawar.s.rajput@gmail.com}
\homepage{dilawars.me}
\setgithub{github.com/dilawar}
\setlinkedin{linkedin.com/dilawars}
\renewcommand\labelitemi{\textbullet}

\begin{document}
<<<<<<< Updated upstream
\hypersetup{urlcolor=blue}
\maketitle

\vspace{-6mm}
\normalsize
=======
>>>>>>> Stashed changes

Experienced system engineer (multiple domains) and fullstack developer with
significant tech lead experience looking for IC roles. I can manage small teams,
build teams, and mentor juniors. FOSS contributor and \href{https://joss.theoj.org/}{reviewer}.

%
% Skills
%
<<<<<<< Updated upstream
\vspace{-3mm}
\section{Skills}
\cvline{Languages}{%
    Rust, C++, Python, PHP, Typescript/JS, SQL, \LaTeX.
    \emph{(familiar)} Haskell, SystemC, Verilog, VHDL.
}
\cvline{Libraries \& Frameworks}{%
    Boost, Win32 API, PyBind11, OpenCV; Python data stack; Leptos;
    Vue3, React, HTMX; Codeigniter, Laravel; Axum, Actix, FastAPI;
    \href{https://github.com/dilawar/HippoApp}{Cordova}, \href{https://github.com/dilawar/sms-forwarder}{Quasar}.
}
\cvline{Simulation \& Modeling}{
    KiCAD, OpenSCAD; ModelSim, NgSpice; MOOSE, Neuron, Smoldyn; PlantUML, TikZ;
}
\cvline{Tech \& Ops}{
    Git, Docker, CMake, PyInfra/Ansible, Shell scripting/Lua; Jenkins/Gitlab Runners;
    Grafana; eBPF; Packaging (nsis, deb, rpm),
    \href{https://build.opensuse.org/users/dilawar}{Open Build Service};
}
\cvline{Databases}{
    PostGreSQL, MariaDB, Sqlite3, DuckDB, VictorialMetrics. {\small
    Phinx, Alembic, SQLModel, SQLX/Diesel.}
}
\cvline{Misc}{
    Literature survery and analysis, Parsing, Network Flows, Graphs, Linear Algebra, Combinatorics,
    Computer Vision, Probabilistic DSA, BDD \& Model Checking, DSP, Routing;
    Android, RTOS, Linux
=======
\ResumeSection{Skills}
\skill{Languages}{
    Rust, C++, Python, PHP, Javascript/Typescript, SQL, \LaTeX.
    \emph{(familiar)} Haskell, VHDL/Verilog/SystemC.
}
\skill{Databases}{
    PostGreSQL, MariaDB, Sqlite3, DuckDB, VictorialMetrics. {\small
    Phinx, Alembic, SQLModel, SQLX/Diesel.}
}
\skill{Libraries \& Frameworks} {
    Boost, PyBind11, Win32 API, GDAL, OpenCV, numpy/scipy stack, leptos.
}
\skill{Web}{
    Vue3, React, HTMX; Codeigniter, Laravel, Axum, Actix, FastAPI;
}
\skill{Modeling and Simulation}{
    PlantUML, TikZ; KiCAD, OpenSCAD; ModelSim, NgSpice; MOOSE, Neuron; Smoldyn.
}
\skill{DevOps}{
    Git, Docker, CMake, PyInfra/ansible, bash/lua; Jenkins, Gitlab Runners;
    Grafana; eBPF based sensors;
    Packaging (nsis, deb, rpm),
    \href{https://build.opensuse.org/users/dilawar}{Open Build Service};
}
\skill{Misc}{
    Parser, Network Flows, Graphs, Linear Algebra \& Combinatorics,
    Computer Vision, Probabilistic DSA, BDD/Model Checking, DSP, Routing.
>>>>>>> Stashed changes
}


%
% Work experience.
%
<<<<<<< Updated upstream
\vspace{-3mm}
\section{Experience}
\cventry{Jan 2025 -- current}{\textbf{Senior Engineer}, Dognosis, Bengaluru}{}{}{}{%
    \cvlistitem{%
        \normalsize
        Added SLAM to existing canine kit that generates 3D model of arena to
        enable certain use-cases for demo-day
    }
    \cvlistitem{%
        \normalsize
        Build data APIs and portals from scratch to collect medical data at remote locations
    }
    \cvlistitem{%
        \normalsize
        Setup hiring pipelines, interviewed and hired 5 engineers to increase team
        sizes to 11 in 3 months
    }
}
\cventry{Dec 2019 -- Dec 2024}{\textbf{Cofounder \& CTO}, Subconscious Compute, Bengaluru}{}{}{}{%
    \cvlistitem{%
        \normalsize
        Cofounded a endpoint cybersecurity startup after my PhD and took it through pre-series A
    }
    \cvlistitem{%
        \normalsize
        Hired and led a team of 15 system engineers to build our flagship endpoint
        security product Shepherd
    }
    \cvlistitem{%
        \normalsize
        Wrote kernel minifilter, designed core algorithms, and setup devops for cross-platform deployment
    }
}
\cventry{2016 -- 2018}{\textbf{Research Fellow \& GSoC Mentor}}{}{}{}{%
    \cvlistitem{%
        \normalsize
        Added various numerical solvers in \href{https://moose.ncbs.res.in}{MOOSE} simulator
        that allowed broader use in multiscale problems
    }
    \cvlistitem{
        \normalsize
        Mentored GSoC participants of INCF for 3 years on GPU/CUDA effort
        resulting in faster simulations
    }
}

\cventry{Jul 2009 -- Jun 2010}{\textbf{Firmware Engineer}, Kritikal Solutions, Noida}{}{}{}{%
    \cvlistitem{%
        \normalsize
        Implemented Kalman filter based image stabilizer that removed most vibration artifacts
        from recorded videos
=======
\ResumeSection{Experience}

\entry{Dognosis}{Senior Engineer}{Bengaluru}{Jan 2025 -- current}
\tech{%
    \details{%
        \item Responsible for improving computational and experimental cancer-detection strategies using dogs.
        \item Building data APIs and portals to collect patient data at remote locations, and helping hardware team to build an experimental arena where trainers involvement is minimized.
        \item I also help in building technical team (technical interviews), infrastructure and devops.
        }
    }

\entry{Subconscious Compute}{Cofounded and CTO}{Bengaluru}{Dec 2019 -- Dec 2024}
\tech{%
    \details{%
    \item Cofounded a endpoint cybersecurity startup  and took it through pre-series A.
        I hired and led a team of 15 system engineers to build its flagship endpoint
        security product Shepherd.

    \item As IC, I wrote kernel minifilter (C++, Win32) and contributed to endpoint
        observability agent (Rust, C++, Java) for cross-platform (Linux, Windows, OSX,
        Android) deployment.
    }
}

\entry{NCBS Bangalore \& INCF}{Research Fellow \& GSoC Mentor}{2016 -- 2018}
\tech{%
    \details{%
    \item To improve the speed of various numerical solvers in the simulator \href{https://moose.ncbs.res.in}{MOOSE}, I mentored GPU/CUDA effort in GSoC. Added SMBL support and modernize build system.

    }
}

\entry{Kritikal Solultions}{Firmware Engineer}{Noida}{Jul 2009 -- Jun 2010}
\tech{%
    \details{%
    \item To remove vibration artifacts from recorded videos, I implemented Kalman filter based image stabilizer.
>>>>>>> Stashed changes
    }
}

%
% Projects
%
\section{Projects}
<<<<<<< Updated upstream
\cvlistitem{%
    Wrote \href{https://ncbs.res.in/hippo}{NCBS Hippo} being used by >1000 people
    on campus. It automatically \& "optimally" schedule annual thesis seminars,
    manages meeting rooms and institute public calendar. Wrote
    accompanying Android App. Hippo saved thousands of) trips and emails to academic office.
=======
\cvlistitem{
    To reduce email chaos and trips to the academic office, I wrote
    \href{https://ncbs.res.in/hippo}{NCBS Hippo} to automatically
    \& "optimally" schedule annual seminars. It also managed room booking,
    institute public calendar. I also wrote accompanying Android App
    (\href{https://play.google.com/store/apps/details?id=com.dilawar.hippo}{Google
    Play}).
>>>>>>> Stashed changes
}
\cvlistitem{%
    Built a \href{https://github.com/BhallaLab/AnimalBehaviour}{Behaviour Box}
    that automated training session making multiple sessions possible in a day!
}
\cvlistitem{%
    Wrote and maintain a few \href{https://crates.io/users/dilawar}{rust
    crates}: stream processing, WMI interface, a few cli utilities
}
<<<<<<< Updated upstream
\cvlistitem{%
    Wrote and maintain a few \href{https://pypi.org/user/dilawar}{python
    packages}: a popular utility to extract
    \href{https://github.com/dilawar/PlotDigitizer}{data from images of plots},
    Notion/Gitlab bridge for internal use,
    a UI for oscilloscope and a simple plagiarism detector
    \href{https://github.com/dilawar/sniffer}{CodeSniffer} as teaching
    assistant
=======
\cvlistitem{
    I wrote and maintain a few \href{https://pypi.org/user/dilawar}{python
    packages}: a utility to extract
    \href{https://github.com/dilawar/PlotDigitizer}{data from images of plots},
    Notion/Gitlab bridge,
    a UI for oscilloscope, and a poor man's plagiarism detector
    \href{https://github.com/dilawar/sniffer}{CodeSniffer}. I also wrote python
    bindings and maintain \href{https://pypi.org/project/smoldyn}{wheels} for
    \href{https://smoldyn.org}{Smoldyn simulator} and
    \href{https://pypi.org/project/pymoose/}{MOOSE simulator}.
>>>>>>> Stashed changes
}
\cvlistitem{%
    Wrote python bindings and maintain \href{https://pypi.org/project/smoldyn}{wheels} for
    two major C++ academic simuators \href{https://smoldyn.org}{Smoldyn} and
    \href{https://pypi.org/project/pymoose/}{MOOSE}
}


%
% EDUCATION
%
\section{Education}
\cventry{2019}{\textbf{PhD}, Computational Neuroscience, NCBS Bangalore (TIFR Mumbai), India}{}{}{}{}
\cventry{2013}{\textbf{PhD}, Digial Systems, IIT Bombay}{}{}{\textbf{withdrawn}}{}
\cventry{2009}{\textbf{Master of Technology}, Electrical Engineering (VLSI), IIT Bombay}{}{}{}{}
% \cventry{2007}{\textbf{BTech}, Electrical Engineering, Dr. MGR ERI, Chennai}{}{}{}{}

\end{document}
